A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-10 doc/draft-01-stokes/04numerical.tex
adding annulus results

\subsection{Eigenvalues of an annulus}

\subsubsection{Spurious eigenvalues}
\label{subsec:spurannulus}

\subsubsection{Convergence study}
\label{subsec:convannulus}

>>>>

\subsection{Eigenvalues of an annulus}
We test our numerical machinery and validate our analytical 
and numerical claims
by comparing the results to the true eigenvalues on the annulus
which are known analytically (see~\cref{sec:annul_dir_exact}).
In all of the examples below, we work on the annulus $r_{1}<r<r_{2}$
with $r_{1} = 1$ and $r_{2} = 1.7$.
If the inner boundary is discretized using $N_{1}$ panels, 
then the outer boundary is discretized using $N_{2} = 
\lceil r_{2}/r_{1} N_{1} \rceil +1$ panels to ensure that the
panels are approximately the same length on both the boundaries. 
The total number of discretization points 
is then given by $N = 16(N_{1} + N_{2})$.
Let $D^{N}_{k}$ denote the linear system corresponding
to the Nystr\"{o}m discretization of
$-2\cD_{k} -2\cW$ using generalized Gaussian quadrature, 
and let $C^{N}_{k}$ denote the linear system corresponding
to the Nystr\"{o}m discretization of 
$-2\cD_{k} - 2i\cS_{k} -2\cW$.
Let $f_{D}^{N}(k) = \text{det}(I+D^{N}_{k})$, and 
$f_{C}^{N}(k) = \text{det}(I+C^{N}_{k})$.

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lsim N^{-20}$, 
and $|k_{C} - k_{0}| \lsim N^{-20}$.
Note that N^{-20} is the observed order of
convergence for Generalized Gaussiuan quadratures for weakly 
singular integrals.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

\subsubsection{Spurious eigenvalues}
\label{subsec:spurannulus}
As noted in~\cref{subsec:dlanalysis},
if $k_{0}$ is a Neumann eigenvalue corresponding to the interior
inclusion, which in our case is the disk $r\leq r_{1}$, then
$f_{D}(N)(k_{0}) is O(\varepsilon)$ even though $k_{0}$ 
is not a Dirichlet eigenvalue of the annulus, i.e.
the integral equation $-\cI - 2\cD_{k} -2\cW$ has a spurious eigenvalue.
In~\cref{fig:spur}, we demonstrate this result and also show that 
$f_{C}^{N}(k_{0}) \neq 0$, i.e., the combined field representation is
robust and invertible at all values of $k$ which are not the Dirichlet
eigenvalues of the annulus.

\subsubsection{Speed}
\label{subsec:speed}
In this section, we demonstrate the O(N\log{N}) scaling of evaluating
$f^{N}_{C}(k)$ as long as $N$ is large enough to resolve the interactions
at the Helmholtz parameter $k$. 
When $N$ is smaller than that, we observe a worse scaling since the
assumption that far-interactions are low-rank is no longer valid at
the tolerance of FLAM.
We plot the timing results corresponding to three different values of 
$k$ in~\cref{fig:speed}.
